Water Management

### 2020-02-12 Paper/paper.tex
further text and removed wrapfigure for now. Looks nicer side by side

\begin{wrapfigure}{l}{0.5\textwidth} 
	\includegraphics[width=0.5\textwidth]{figures/rainfall-real-data.eps}

@@

\end{wrapfigure}

@@

As shown in \ref{fig:optimalIrrigationPolicy-real-data} the changed distribution of rainfalls also has an effect on the optimal irrigation policy since it depends ocn the expected amount of rain.
\begin{wrapfigure}{l}{0.5\textwidth} 
	\includegraphics[width=0.5\textwidth]{figures/optimalIrrigationPolicy-real-data.eps}
\end{wrapfigure}

>>>>

\begin{figure}[h]
	\includegraphics[width=1\textwidth]{figures/rainfall-real-data.eps}

@@

	\includegraphics[width=1\textwidth]{figures/optimalIrrigationPolicy-real-data.eps}

@@

As shown in \ref{fig:optimalIrrigationPolicy-real-data} the changed distribution of rainfalls also has an effect on the optimal irrigation policy since it depends on the expected amount of rain.
Due to the higher expected value of rainfalls the optimal irrigation policy is steeper over the water level compared to the simulated rainfall.
